---
title: "Chapter 3"
author: "Ryan Fabricius"
date: "5/14/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Load Libraries
library(dplyr)
library(sparklyr)
library(dbplot)
library(corrr)
library(ggplot2)
```

```{r}
# Connect to Spark
sc <- spark_connect(master = "local", version = "2.4")
```

```{r}
# Prime Spark with mtcars dataset
cars <- copy_to(sc, mtcars)
```

```{r}
# Use dplyr > SQL
summarise_all(cars, mean)
```

```{r}
# Inspect SQL Query
summarise_all(cars, mean) %>% 
        show_query()
```

```{r}
# Group by Transmission type
cars %>%
  mutate(transmission = ifelse(am == 0, "automatic", "manual")) %>%
  group_by(transmission) %>%
  summarise_all(mean)
```

When you want to perform an operation from dplyr that is not yet available in Spark, there is usually a Hive function within Spark to accomplish what you need.

```{r}
# Using a Hive function
summarise(cars, mpg_percentile = percentile(mpg, 0.25))
```

```{r}
# Visualize Query
summarise(cars, mpg_percentile = percentile(mpg, 0.25)) %>% 
        show_query()
```

```{r}
# Passing Array of inputs
summarise(cars, mpg_percentile = percentile(mpg, array(0.25, 0.5, 0.75)))
```

```{r}
# Use explode function to seperate array values into their own record
summarise(cars, mpg_percentile = percentile(mpg, array(0.25, 0.5, 0.75))) %>%
  mutate(mpg_percentile = explode(mpg_percentile))
```

```{r}
# Use correlation Spark functions
correlate(cars, use = "pairwise.complete.obs", method = "pearson")
```

```{r}
# Shave removes duplicated values
correlate(cars, use = "pairwise.complete.obs", method = "pearson") %>% 
        shave(., upper = T)
```

```{r}
# Only bring in aggregated results to graph
car_group <- cars %>%
  group_by(cyl) %>%
  summarise(mpg = sum(mpg, na.rm = TRUE)) %>%
  collect() %>%
  print()
```

```{r}
# Graph aggregated results
ggplot(aes(as.factor(cyl), mpg), data = car_group) + 
  geom_col(fill = "#999999") + coord_flip()
```

The dbplot package provides helper functions for plotting with remote data. The R code dbplot that’s used to transform the data is written so that it can be translated into Spark. It then uses those results to create a graph using the ggplot2 package where data transformation and plotting are both triggered by a single function.

```{r}
# Plotting using dbplot
dbplot_raster(cars, mpg, wt, resolution = 16)
```

```{r}
# Disconnect from Spark
spark_disconnect(sc)
```































































